ASTRONOMICAL INFERENCE WITH DIFFUSIVE NESTED SAMPLING

### 2013-11-15 abstract.tex
Brain dump

%%%%%  The title of your contribution in all capital letters.
\title{TITLE OF YOUR CONTRIBUTION}

%%%%%  Author's name (underline presenter's author)            
\author{\underline{F. Author}$^{1,2}$, S. Author$^{3}$\\
        (1) First Institution\\
        (2) Second Institution\\
        (3) Third Institution\\
        (You might put here additional information: e-mail,
         URL, etc)
       }

\date{date}
\maketitle

%%%%%               Abstract begins here                      
\begin{abstract}
\noindent
In this work we show how to calculate the answer to the Ultimate Question of Life, the Universe and Everything using a combination of Bayes rule and MaxEnt:
\begin{gather}
P(H|D,I) = \frac{P(D|H,I) \, P(H|I)}{P(D|I)}
\\
\mathcal{H} = - \sum_i p_i \ln \frac{p_i}{q_i}
\end{gather}
and a very large organic computer.

@@

%%%%%       OPTIONAL: Key Words (delete if not used)   
\medskip\noindent{Key Words: }
{Jaynes, Deep Thought, Marsupials}
%%%%%        END of Key Words

>>>>

%%%%%  The title of your contribution in all capital letters.
\title{ASTRONOMICAL INFERENCE WITH DIFFUSIVE NESTED SAMPLING}

%%%%%  Author's name (underline presenter's author)            
\author{\underline{Brendon J. Brewer}$^{1}$\\
        (1) Department of Statistics, The University of Auckland\\
	\\
        {\tt http://stat.auckland.ac.nz/\~{ }brewer/}
       }

\date{}
\maketitle

%%%%%               Abstract begins here                      
\begin{abstract}
\noindent

Many standard problems in astronomy (e.g. the processing of images to produce
``catalogs'') are best understood as inference problems. In principle at least,
we should calculate the posterior distribution over a suitable hypothesis space,
rather than inventing ad-hoc procedures.

I will describe the Diffusive Nested Sampling method, which is a variant of
Nested Sampling that retains the flexibility of Markov Chain Monte Carlo
exploration of the hypothesis space.

Talk about the StarField project
Talk about Reverberation Mapping
Talk about how Nested Sampling is hard when you need to compress so far
Talk about reversible jump

@@

%%%%%       OPTIONAL: Key Words (delete if not used)   
\medskip\noindent{Key Words: }
{Bayesian Inference, Markov Chain Monte Carlo}
%%%%%        END of Key Words
